Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-23 sattose/paper.tex
Added relation table

>>>>

\begin{table}[H]
\begin{tabular}{|l|l|l|}
\textbf{Relation}  & \textbf{Amount} & \textbf{Percentage} \\
FIRSTCOUSIN        & 695             & 2,02                \\
SUPERCLASS         & 488             & 1,42                \\
COMMONHIERARCHY    & 442             & 1,29                \\
UNRELATED          & 13537           & 39,39               \\
EXTERNALSUPERCLASS & 2402            & 6,99                \\
SIBLING            & 5978            & 17,39               \\
SAMEMETHOD         & 2456            & 7,15                \\
SAMECLASS          & 8341            & 24,27               \\
ANCESTOR           & 28              & 0,08
\end{tabular}
\end{table}
